Automated topic naming to support analysis of software maintenance activities

### 2010-08-19 icse/icse2011.tex
changes to visualization discussion. Added notes on releases of both dbs.

\documentclass[]{sig-alternate}
 \usepackage{booktabs}
\usepackage[caption=false]{subfig}
 \usepackage[colorinlistoftodos,backgroundcolor=yellow,disable]{todonotes} %disable
 \usepackage{color}

@@

\conferenceinfo{ICSE}{'11 Waikiki, Hawaii USA}
\numberofauthors{5}
\author{
\alignauthor 
Abram Hindle\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{ahindle@uwaterloo.ca}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor Richard C. Holt \\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{holt@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

@@

\subsection{Summary of techniques}
While unsupervised techniques (LSI and LDA are both unsupervised) are appealing in their lack of human intervention, and thus lower effort, supervised learners have the advantage of domain knowledge which typically means improved results.

Very rarely did \textsf{exp2} and \textsf{exp3} (naive word matching) ever perform as well as the supervised machine learners. For MaxDB, \textit{reliability} was slightly better detected using the static word list of \textsf{exp2}. In general, the machine learners and \textsf{exp3} did better than \textsf{exp2} for both MaxDB and MySQL. For both MySQL and MaxDB \textit{usability} was better served by \textsf{exp2}. \textit{Usability} was a very infrequent label, however, which made it difficult to detect in any case.

@@

\section{Using \textbf{Nomen} to understand software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
Using the classification results from the previous sections, we evaluated two research questions:
\begin{enumerate}
\item Do label frequencies change over time? That is, is a certain quality of more interest at one point in the life-cycle than some other? 
\item  Do the different projects differ in their relative topic interest? That is, is a particular quality more important to one project than the other projects?  
\end{enumerate}

@@

For example, in Fig. \ref{fig:mysql-timeline}, we see that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labeled topics, since these NFRs have more intensely shaded boxes. We note that the gap in the MaxDB data is due to an interruption in the source data, having to do with the infrastructure for releasing data, rather than specific occurrences in the project.
\todo[inline]{can I pin this down more ?}

\todo[inline]{try to pin down these reasons below}%  MySQL 3.23 was put on maintenance.
% 
% MySQL forks repositories per every version and 3.23 was supported for a
% long time. there was 4.0 4.1 5.0 5.1
% 
% This is the MySQL 3.23 branch
% 
% Same thing with MaxDB 7.5
% 7.6 is in a different repository

>>>>

\documentclass[]{sig-alternate}
 \usepackage{booktabs}
\usepackage[caption=false]{subfig}
 \usepackage[colorinlistoftodos,backgroundcolor=yellow]{todonotes} %disable
 \usepackage{color}

@@

\conferenceinfo{ICSE}{'11 Waikiki, Hawaii, USA}
\numberofauthors{5}
\author{
\alignauthor 
Abram Hindle\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{ahindle@uwaterloo.ca}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor Richard C. Holt \\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{holt@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

@@

@@

\subsection{Summary of techniques}
While unsupervised techniques (LSI and LDA are both unsupervised) are appealing in their lack of human intervention, and thus lower effort, supervised learners have the advantage of domain knowledge which typically means improved results. Our manual annotations were fairly quick to do, taking on average five minutes per 30 day period.

Very rarely did \textsf{exp2} and \textsf{exp3} (naïve word matching) ever perform as well as the supervised machine learners. For MaxDB, \textit{reliability} was slightly better detected using the static word list of \textsf{exp2}. 
In general, the machine learners and \textsf{exp3} did better than \textsf{exp2} for both MaxDB and MySQL. 
For both MySQL and MaxDB \textit{usability} was better served by \textsf{exp2}. 
\textit{Usability} was a very infrequent label, however, which made it difficult to detect in any case.

\section{Using \textbf{Nomen} to understand software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}

Using the classification results from the previous sections, we evaluated two research questions:
\begin{enumerate}
\item Do label frequencies change over time? That is, is a certain quality of more interest at one point in the life-cycle than some other? 
\item  Do the different projects differ in their relative topic interest? That is, is a particular quality more important to one project than the other projects?  
\end{enumerate}

@@

\textbf{Understanding the figures} -- For example, in Fig. \ref{fig:mysql-timeline}, we see that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labeled topics, since these NFRs have more intensely shaded boxes. We note that the gap in the MaxDB data is due to an interruption in the source data, having to do with the infrastructure for releasing developer artifacts, rather than specific occurrences in the project.
\todo[inline]{can I pin this down more ?}
There are more \textsf{None} labels in MaxDB because a number of topics were to do with code cleanup or automated checking using tools like \texttt{sutcheck}, a tool-specific to the development process at MaxDB.

\textbf{Timeline of key events} -- Figs. \ref{} show key events for each of our projects. Several external events (external to `normal' development activity, that is) affected our projects. For example, both projects show a high number of NFRs recognized at the first period of analysis. This is due to our window choice: we deliberately targeted our analysis to 
MySQL 3.23 First announced Major update \& End-of life
MaxDB 7.500 First announced

Note that MySQL's release process was haphazard at this point: they would release a patch version whenever the need arose. By version 5.1, the company moved to a milestone release, with new releases targeted for every six months.

\todo[inline]{Does our visualization capture the entire timeline?}

\todo[inline]{try to pin down these reasons below}
%  MySQL 3.23 was put on maintenance.
% 
% MySQL forks repositories per every version and 3.23 was supported for a
% long time. there was 4.0 4.1 5.0 5.1
% 
% This is the MySQL 3.23 branch
% 
% Same thing with MaxDB 7.5
% 7.6 is in a different repository
